My title

### 2024-12-03 paper/paper.qmd
Finish the final script (modelling)

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Kevn Shao
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

## Outcome variables

@@

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Kevn Shao
thanks: "Code and data are available at: https://github.com/KevinShao1357/Toronto_Daily_Shelter_And_Overnight_Service_Modelling.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

## Outcome variables (And Estimand)

@@

Since we are trying to constructing a multivariate linear regression model, our estimand is the response variable, which is the the number of occupied beds during a day (can be understood as the demand of beds) in a location that provides daily shelter or overnight service.

@@

Now we start to create the multivariate linear regression model, with the set predictor and response variables.
